Variable Selection in Convex Function Estimation

### 2014-05-05 tex/scam/appendix.tex
paper modifications

Suppose $\lambda_n \geq \mathbf{c} s Lb \sigma  \sqrt{ \frac{1}{n} \log^2 np}$, then with probability at least $ 1 - \frac{C}{n}$, for all $k \in S^c$, and for all $i'=1,...,n$:
\[
\lambda_n > \Big| \frac{1}{2n}\hat{r}^\tran \mathbf{1}_{(i':n)} \Big|
\]

@@

Because $w_i$ is subgaussian, $|w_i| \leq \mathbf{c} \sigma \sqrt{\log \frac{2}{\delta}}$ with probability at most $1-\delta$. By union bound across $i=1,...,n$, we have that $\| w\|_\infty \leq \mathbf{c} \sigma \sqrt{ \log \frac{2}{\delta}}$ with probability at most $1 - n \delta$.

We now put this together and take another union bound across all $j$ and all $i'$:
\begin{align*}
\| \hat{r} \|_\infty &\leq \mathbf{c} (sLb + \sigma \sqrt{ \log \frac{2}{\delta}}) \\
      &\leq \mathbf{c} sLb \sigma \sqrt{\log \frac{2}{\delta}}
\end{align*}
with probability at least $1 - n^2 p \delta$. We supposed that both $sLb \geq 2$ and $\sigma\sqrt{\log \frac{2}{\delta}} \geq 2$.

@@

\begin{align*}
| \frac{1}{n} \hat{r}^\tran \mathbf{1}| &\leq 2 sLb \sqrt{\frac{1}{n} \log \frac{2}{\delta}} + 2 \sigma \sqrt{\frac{1}{n} \log \frac{2}{\delta}} \\
  &\leq \mathbf{c} sLb \sigma \sqrt{\frac{1}{n} \log \frac{2}{\delta}} 
\end{align*}
with probability at least $1-2\delta$.\\

@@

Taking an union bound across previous events, we have that with probability at least $1 - 3n^2 p \delta$, for all $j \in S^c$, for all $i'=1,...,n$:
\begin{align*}
\Big|\frac{1}{n} \hat{r}^\tran \mathbf{1}_{(i':n)} \Big| &\leq
  \mathbf{c} sLb \sigma \sqrt{\frac{1}{n} \log \frac{2}{\delta}} 
\end{align*}
Setting $\delta = \frac{1}{n^3 p}$ gives the desired result.

@@

\begin{theorem}
\label{thm:convex_consistent}
Let $\hat{f}$ be the minimizer of the restricted regression with $\lambda \leq \mathbf{c} sLb\sqrt{ \frac{1}{n} \log^2 np}$.

Then, with probability at least $1-\delta$,
\begin{align}
\|f_0 - \hat{f} \|_P^2 - \| f_0 - f^* \|_P^2 
&\leq \mathbf{c} (Lb)^3\sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{np}{\delta}}
\end{align}

@@

Using Lemma~\ref{lem:remove_centering}, we can remove $\bar{f}^*$ from the LHS. With probability at least $1 - \delta$:
\begin{align}
\label{eqn:first_step_inequality}
\|f_0 - \hat{f} \|_n^2 - \| f_0 - f^* \|_n^2 
   &\leq 2 \langle w, \hat{f} - f^* + \bar{f}^* \rangle + \lambda 4 s L b + \mathbf{c}(sLb)^2 \frac{1}{n} \log \frac{2}{\delta}
\end{align}

@@

According to theorem~\ref{thm:chaining}, for all $\epsilon > \frac{1}{\sqrt{n}}\sigma \mathbf{c} \int_0^R \sqrt{ \log N_2(t, \mathcal{G}) }dt \vee R$,
\[
P\Big( \sup_{h \in \mathcal{G}} \langle w, h \rangle_n \geq \epsilon \Big) \leq
  4 \exp \Big( - \frac{ n \epsilon^2}{ \mathbf{c} R^2 \sigma^2} \Big)
\]
where $R = 4sLb$ for our purpose.

Restated, we have that, with probablity at least $1-\delta$,
\[
\sup_{h \in \mathcal{G}} | \langle w, h \rangle_n | \leq 
   \mathbf{c} R \sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta}} + 
      \Big( \int_0^R \sqrt{\log N_2(t, \mathcal{G})}dt \vee R \Big)\, 
       \mathbf{c} \sigma \sqrt{\frac{1}{n}} 
\]

@@

\begin{align*}
\int_0^R \sqrt{\log N_{\|\cdot\|_n}(t, \mathcal{G})} dt &\leq 
      \sqrt{C s^{1.5} b L} \int_0^R t^{-1/4} dt \\ 
 &= \sqrt{C s^{1.5} b L} \, \frac{4}{3} R^{3/4} \\
 &= \sqrt{C s^{1.5} b L} \, \mathbf{c} (sLb)^{3/4} \\
 &\leq \mathbf{c} (s b L)^2
\end{align*}

Coming back, we have, with probability at least $1-\delta$,
\begin{align*}
\sup_{h \in \mathcal{G}} | \langle w, h \rangle | &\leq 
    \mathbf{c} sLb \sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta} } + 
    \mathbf{c} (sLb)^2 \sigma \sqrt{ \frac{1}{n} } \\
 &\leq \mathbf{c} (sLb)^2\sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta} }
\end{align*}

Plugging this result into equation~\ref{eqn:first_step_inequality} and using an union bound, we get, with probability at least $1 - 2\delta$:
\begin{align}
\|f_0 - \hat{f} \|_n^2 - \| f_0 - f^* \|_n^2 
   &\leq \mathbf{c} (sLb)^2 \sigma \sqrt{\frac{1}{n} \log \frac{4}{\delta}} 
   + \lambda 4 s L b + \mathbf{c}(sLb)^2 \frac{1}{n} \log \frac{2}{\delta} \nonumber\\
\|f_0 - \hat{f} \|_n^2 - \| f_0 - f^* \|_n^2 
   &\leq \mathbf{c} (sLb)^2 \sigma \sqrt{\frac{1}{n} \log \frac{4}{\delta}} 
   + \lambda 4 s L b    \label{eqn:second_step_inequality}
\end{align}

@@

\begin{align}
\|f_0 - \hat{f} \|_P^2 - \| f_0 - f^* \|_P^2 
   &\leq \mathbf{c} (sLb)^2 \sigma \sqrt{\frac{1}{n} \log \frac{4}{\delta}} 
 +\lambda 4 s L b + \mathbf{c} (Lb)^3 \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}}
    \nonumber \\
&\leq \mathbf{c} (Lb)^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}} + \lambda 4 sLb
\end{align}

Substituting in $\lambda \leq \mathbf{c} sLb \sqrt{\frac{1}{n} \log^2 np}$ and we get the desired result.

@@

\begin{theorem}
\label{thm:concave_consistent}
Let $\hat{g}_k$ denote the minimizer of the concave postprocessing with $\lambda \leq \mathbf{c} sLb \sqrt{\frac{1}{n} \log^2 np}$.\\

@@

Then, with probability at least $1- s\delta$, for all $k=1,...,s$:\\
\[
\| f_0 - f^* - \hat{g}_k \|_P^2 - \| f_0 - f^* - g^*_k \|_P^2 \leq  \mathbf{c}(Lb)^{2.5} \sigma^{0.5} \sqrt[4]{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} 
\]
\end{theorem}

@@

Using the chaining result (theorem~\ref{thm:chaining}), setting $s=1$, we have, with probability at least $1-\delta$,
\begin{align*}
\| f_0 - \hat{f} - \hat{g}_k \|_n^2 - \|f_0 - \hat{f} - g^*_k \|_n^2 &\leq
  \mathbf{c} (Lb)^2 \sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta} }+ \lambda 2 Lb
\end{align*}

Using the uniform convergence result (lemma~\ref{lem:uniform_convergence}), we have, with probability at least $1-2\delta$:
\begin{align*}
\| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \|f_0 - \hat{f} - g^*_k \|_P^2 &\leq
  \mathbf{c} (Lb)^2 \sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta} }+ \lambda 2 Lb +
  \mathbf{c} (Lb)^3 \sqrt{\frac{s^5}{n^{4/5}} \log \frac{2}{\delta} } \\
 &\leq \mathbf{c}(Lb)^3\sigma \sqrt{\frac{s^5}{n^{4/5}} \log \frac{4}{\delta}}+ \lambda 2 Lb
\end{align*}

Plugging in $\lambda \leq \sqrt{ \frac{1}{n} \log^2 np}$:
\begin{align*}
\| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \|f_0 - \hat{f} - g^*_k \|_P^2 &
\leq \mathbf{c}(Lb)^3\sigma \sqrt{\frac{s^5}{n^{4/5}} \log \frac{4}{\delta}}+ 
    2Lb \sqrt{\frac{1}{n} \log^2 np}\\
\| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \|f_0 - \hat{f} - g^*_k \|_P^2 &
\leq \mathbf{c}(Lb)^3\sigma \sqrt{\frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} \\
\end{align*}

@@

\begin{align*}
\| f_0 - \hat{f} - g^*_k \|_P^2 - \| f_0 - f^* - g^*_k\|_P^2 &\leq 
    \| f_0 - \hat{f} \|_P^2 - \|f_0 - f^*\|_P^2 - 2\langle f_0 - \hat{f}, g^*_k \rangle
   + 2 \langle f_0 - f^*, g^*_k \rangle \\
 &\leq \mathbf{c} (Lb)^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} + 
    2 | \langle \hat{f} - f^*, g^*_k \rangle |  \\
 &\leq  \mathbf{c} (Lb)^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} +
    2 \| \hat{f} - f^* \|_P \| g^*_k \|_P \\
&\leq  \mathbf{c} (Lb)^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} +
   \mathbf{c}(Lb) \sqrt{(Lb)^3\sigma \sqrt{ 
                   \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} }\\
&\leq  \mathbf{c}(Lb) \sqrt{(Lb)^3\sigma \sqrt{ 
                   \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} }\\
\end{align*}

@@

\textbf{Step 3.} Collecting the results from Step 1 and Step 2, we have, with probability at least $1-2\delta$:
\begin{align*}
\| f_0 - f^* - \hat{g}_k \|_P^2 - \|f_0 - f^* - g^*_k \|_P^2 \leq
   \mathbf{c}(Lb)^{2.5} \sigma^{0.5} 
     \sqrt[4]{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} 
\end{align*}

@@

\begin{lemma}
\label{lem:uniform_convergence}
With probability at least $1-\delta$:
\begin{align*}
\sup_{f \in \mathcal{C}^s_L} \Big| \| f_0 - f \|^2_n - \|f_0 - f \|^2_P\Big| \leq
   \mathbf{c} (Lb)^3 \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}}
\end{align*}

@@

We will set $\epsilon = \frac{1}{n^{2/5}} (C s^{0.5} L b)^2$. 
Therefore:
\begin{align*}
\sup_{h_\epsilon} \Big|  \|h_\epsilon\|^2_n - \|h_\epsilon\|^2_P \Big| &\leq
   (8sLb)^2 \sqrt{ \frac{1}{cn} \big(\log \frac{2}{\delta} 
        + s n^{1/5}  \big) } \\
  &\leq (8Lb)^2 \sqrt{ \frac{s^5}{cn^{4/5}} \log \frac{2}{\delta} }
\end{align*}
And
\begin{align*}
\sup_{h \in \mathcal{G}}  \Big| \|h\|^2_n - \|h\|^2_P \Big| &\leq 
\sup_{h_\epsilon} \Big| \|h_\epsilon\|^2_n - \|h_\epsilon\|^2_P \Big| 
        + \frac{1}{n^{2/5}} C^2 s^2 (Lb)^3 \\
  &\leq (8Lb)^2 \sqrt{ \frac{s^5}{c n^{4/5}} \log \frac{2}{\delta}}
     + (CLb)^2 \sqrt{ \frac{s^4}{n^{4/5}} } \\
  &\leq \mathbf{c} (Lb)^3 \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}}
\end{align*}

@@

Then, with probability at least $1 - 2\delta$,
\[
\Big | \| f_0 - f^* \|_n^2 - \| f_0 - f^* + \bar{f}^* \|_n^2 \Big| \leq
    \mathbf{c} (sLb)^2 \frac{1}{n} \log \frac{4}{\delta}
\]
\end{lemma}

@@

\begin{align*}
| \bar{f}^* | | \bar{f}_0 | &\leq \mathbf{c} (sLb)^2 \frac{1}{n} \log \frac{2}{\delta} \\
\bar{f}^{*2} &\leq \mathbf{c} (sLb)^2 \frac{1}{n} \log \frac{2}{\delta}
\end{align*}

Therefore, with probability at least $1 - 2\delta$,
\[
\|f_0 - f^*\|_n^2 - \mathbf{c} (sLb)^2 \frac{1}{n} \log \frac{2}{\delta} \leq
    \| f_0 - f^* + \bar{f}^* \|_n^2 \leq 
\|f_0 - f^*\|_n^2 + \mathbf{c} (sLb)^2 \frac{1}{n} \log \frac{2}{\delta}
\]

>>>>

Suppose $\lambda_n \geq c s Lb \sigma  \sqrt{ \frac{1}{n} \log^2 np}$, then with probability at least $ 1 - \frac{C}{n}$, for all $k \in S^c$, and for all $i'=1,...,n$:
\[
\lambda_n > \Big| \frac{1}{2n}\hat{r}^\tran \mathbf{1}_{(i':n)} \Big|
\]

@@

Because $w_i$ is subgaussian, $|w_i| \leq c \sigma \sqrt{\log \frac{2}{\delta}}$ with probability at most $1-\delta$. By union bound across $i=1,...,n$, we have that $\| w\|_\infty \leq c \sigma \sqrt{ \log \frac{2}{\delta}}$ with probability at most $1 - n \delta$.

We now put this together and take another union bound across all $j$ and all $i'$:
\begin{align*}
\| \hat{r} \|_\infty &\leq c (sLb + \sigma \sqrt{ \log \frac{2}{\delta}}) \\
      &\leq c sLb \sigma \sqrt{\log \frac{2}{\delta}}
\end{align*}
with probability at least $1 - n^2 p \delta$. We supposed that both $sLb \geq 2$ and $\sigma\sqrt{\log \frac{2}{\delta}} \geq 2$.

@@

\begin{align*}
| \frac{1}{n} \hat{r}^\tran \mathbf{1}| &\leq 2 sLb \sqrt{\frac{1}{n} \log \frac{2}{\delta}} + 2 \sigma \sqrt{\frac{1}{n} \log \frac{2}{\delta}} \\
  &\leq c sLb \sigma \sqrt{\frac{1}{n} \log \frac{2}{\delta}} 
\end{align*}
with probability at least $1-2\delta$.\\

@@

Taking an union bound across previous events, we have that with probability at least $1 - 3n^2 p \delta$, for all $j \in S^c$, for all $i'=1,...,n$:
\begin{align*}
\Big|\frac{1}{n} \hat{r}^\tran \mathbf{1}_{(i':n)} \Big| &\leq
  c sLb \sigma \sqrt{\frac{1}{n} \log \frac{2}{\delta}} 
\end{align*}
Setting $\delta = \frac{1}{n^3 p}$ gives the desired result.

@@

\begin{theorem}
\label{thm:convex_consistent}
Let $\hat{f}$ be the minimizer of the restricted regression with $\lambda \leq c sLb\sqrt{ \frac{1}{n} \log^2 np}$.

Then, with probability at least $1-\delta$,
\begin{align}
\|f_0 - \hat{f} \|_P^2 - \| f_0 - f^* \|_P^2 
&\leq c (Lb)^3\sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{np}{\delta}}
\end{align}

@@

Using Lemma~\ref{lem:remove_centering}, we can remove $\bar{f}^*$ from the LHS. With probability at least $1 - \delta$:
\begin{align}
\label{eqn:first_step_inequality}
\|f_0 - \hat{f} \|_n^2 - \| f_0 - f^* \|_n^2 
   &\leq 2 \langle w, \hat{f} - f^* + \bar{f}^* \rangle + \lambda 4 s L b + c(sLb)^2 \frac{1}{n} \log \frac{2}{\delta}
\end{align}

@@

According to theorem~\ref{thm:chaining}, for all $\epsilon > \frac{1}{\sqrt{n}}\sigma c \int_0^R \sqrt{ \log N_2(t, \mathcal{G}) }dt \vee R$,
\[
P\Big( \sup_{h \in \mathcal{G}} \langle w, h \rangle_n \geq \epsilon \Big) \leq
  4 \exp \Big( - \frac{ n \epsilon^2}{ c R^2 \sigma^2} \Big)
\]
where $R = 4sLb$ for our purpose.

Restated, we have that, with probablity at least $1-\delta$,
\[
\sup_{h \in \mathcal{G}} | \langle w, h \rangle_n | \leq 
   c R \sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta}} + 
      \Big( \int_0^R \sqrt{\log N_2(t, \mathcal{G})}dt \vee R \Big)\, 
       c \sigma \sqrt{\frac{1}{n}} 
\]

@@

\begin{align*}
\int_0^R \sqrt{\log N_{\|\cdot\|_n}(t, \mathcal{G})} dt &\leq 
      \sqrt{C s^{1.5} b L} \int_0^R t^{-1/4} dt \\ 
 &= \sqrt{C s^{1.5} b L} \, \frac{4}{3} R^{3/4} \\
 &= \sqrt{C s^{1.5} b L} \, c (sLb)^{3/4} \\
 &\leq c (s b L)^2
\end{align*}

Coming back, we have, with probability at least $1-\delta$,
\begin{align*}
\sup_{h \in \mathcal{G}} | \langle w, h \rangle | &\leq 
   c sLb \sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta} } + 
    c (sLb)^2 \sigma \sqrt{ \frac{1}{n} } \\
 &\leq c (sLb)^2\sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta} }
\end{align*}

Plugging this result into equation~\ref{eqn:first_step_inequality} and using an union bound, we get, with probability at least $1 - 2\delta$:
\begin{align}
\|f_0 - \hat{f} \|_n^2 - \| f_0 - f^* \|_n^2 
   &\leq c (sLb)^2 \sigma \sqrt{\frac{1}{n} \log \frac{4}{\delta}} 
   + \lambda 4 s L b + c (sLb)^2 \frac{1}{n} \log \frac{2}{\delta} \nonumber\\
\|f_0 - \hat{f} \|_n^2 - \| f_0 - f^* \|_n^2 
   &\leq c (sLb)^2 \sigma \sqrt{\frac{1}{n} \log \frac{4}{\delta}} 
   + \lambda 4 s L b    \label{eqn:second_step_inequality}
\end{align}

@@

\begin{align}
\|f_0 - \hat{f} \|_P^2 - \| f_0 - f^* \|_P^2 
   &\leq c (sLb)^2 \sigma \sqrt{\frac{1}{n} \log \frac{4}{\delta}} 
 +\lambda 4 s L b + c (Lb)^3 \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}}
    \nonumber \\
&\leq c (Lb)^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}} + \lambda 4 sLb
\end{align}

Substituting in $\lambda \leq c sLb \sqrt{\frac{1}{n} \log^2 np}$ and we get the desired result.

@@

\begin{theorem}
\label{thm:concave_consistent}
Let $\hat{g}_k$ denote the minimizer of the concave postprocessing with $\lambda \leq c sLb \sqrt{\frac{1}{n} \log^2 np}$.\\

@@

Then, with probability at least $1- s\delta$, for all $k=1,...,s$:\\
\[
\| f_0 - f^* - \hat{g}_k \|_P^2 - \| f_0 - f^* - g^*_k \|_P^2 \leq  c (Lb)^{2.5} \sigma^{0.5} \sqrt[4]{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} 
\]
\end{theorem}

@@

Using the chaining result (theorem~\ref{thm:chaining}), setting $s=1$, we have, with probability at least $1-\delta$,
\begin{align*}
\| f_0 - \hat{f} - \hat{g}_k \|_n^2 - \|f_0 - \hat{f} - g^*_k \|_n^2 &\leq
  c (Lb)^2 \sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta} }+ \lambda 2 Lb
\end{align*}

Using the uniform convergence result (lemma~\ref{lem:uniform_convergence}), we have, with probability at least $1-2\delta$:
\begin{align*}
\| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \|f_0 - \hat{f} - g^*_k \|_P^2 &\leq
  c (Lb)^2 \sigma \sqrt{ \frac{1}{n} \log \frac{4}{\delta} }+ \lambda 2 Lb +
  c (Lb)^3 \sqrt{\frac{s^5}{n^{4/5}} \log \frac{2}{\delta} } \\
 &\leq c (Lb)^3\sigma \sqrt{\frac{s^5}{n^{4/5}} \log \frac{4}{\delta}}+ \lambda 2 Lb
\end{align*}

Plugging in $\lambda \leq \sqrt{ \frac{1}{n} \log^2 np}$:
\begin{align*}
\| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \|f_0 - \hat{f} - g^*_k \|_P^2 &
\leq c (Lb)^3\sigma \sqrt{\frac{s^5}{n^{4/5}} \log \frac{4}{\delta}}+ 
    2Lb \sqrt{\frac{1}{n} \log^2 np}\\
\| f_0 - \hat{f} - \hat{g}_k \|_P^2 - \|f_0 - \hat{f} - g^*_k \|_P^2 &
\leq c (Lb)^3\sigma \sqrt{\frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} \\
\end{align*}

@@

\begin{align*}
\| f_0 - \hat{f} - g^*_k \|_P^2 - \| f_0 - f^* - g^*_k\|_P^2 &\leq 
    \| f_0 - \hat{f} \|_P^2 - \|f_0 - f^*\|_P^2 - 2\langle f_0 - \hat{f}, g^*_k \rangle
   + 2 \langle f_0 - f^*, g^*_k \rangle \\
 &\leq c (Lb)^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} + 
    2 | \langle \hat{f} - f^*, g^*_k \rangle |  \\
 &\leq  c (Lb)^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} +
    2 \| \hat{f} - f^* \|_P \| g^*_k \|_P \\
&\leq  c (Lb)^3 \sigma \sqrt{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} +
   c (Lb) \sqrt{(Lb)^3\sigma \sqrt{ 
                   \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} }\\
&\leq  c (Lb) \sqrt{(Lb)^3\sigma \sqrt{ 
                   \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} }\\
\end{align*}

@@

\textbf{Step 3.} Collecting the results from Step 1 and Step 2, we have, with probability at least $1-2\delta$:
\begin{align*}
\| f_0 - f^* - \hat{g}_k \|_P^2 - \|f_0 - f^* - g^*_k \|_P^2 \leq
   c (Lb)^{2.5} \sigma^{0.5} 
     \sqrt[4]{ \frac{s^5}{n^{4/5}} \log^2 \frac{4np}{\delta}} 
\end{align*}

@@

\begin{lemma}
\label{lem:uniform_convergence}
With probability at least $1-\delta$:
\begin{align*}
\sup_{f \in \mathcal{C}^s_L} \Big| \| f_0 - f \|^2_n - \|f_0 - f \|^2_P\Big| \leq
   c (Lb)^3 \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}}
\end{align*}

@@

We will set $\epsilon = \frac{1}{n^{2/5}} (C s^{0.5} L b)^2$. 
Therefore:
\begin{align*}
\sup_{h_\epsilon} \Big|  \|h_\epsilon\|^2_n - \|h_\epsilon\|^2_P \Big| &\leq
   (8sLb)^2 \sqrt{ \frac{1}{cn} \big(\log \frac{2}{\delta} 
        + s n^{1/5}  \big) } \\
  &\leq (8Lb)^2 \sqrt{ \frac{s^5}{cn^{4/5}} \log \frac{2}{\delta} }
\end{align*}
And
\begin{align*}
\sup_{h \in \mathcal{G}}  \Big| \|h\|^2_n - \|h\|^2_P \Big| &\leq 
\sup_{h_\epsilon} \Big| \|h_\epsilon\|^2_n - \|h_\epsilon\|^2_P \Big| 
        + \frac{1}{n^{2/5}} C^2 s^2 (Lb)^3 \\
  &\leq (8Lb)^2 \sqrt{ \frac{s^5}{c n^{4/5}} \log \frac{2}{\delta}}
     + (CLb)^2 \sqrt{ \frac{s^4}{n^{4/5}} } \\
  &\leq c (Lb)^3 \sqrt{ \frac{s^5}{n^{4/5}} \log \frac{2}{\delta}}
\end{align*}

@@

Then, with probability at least $1 - 2\delta$,
\[
\Big | \| f_0 - f^* \|_n^2 - \| f_0 - f^* + \bar{f}^* \|_n^2 \Big| \leq
    c (sLb)^2 \frac{1}{n} \log \frac{4}{\delta}
\]
\end{lemma}

@@

\begin{align*}
| \bar{f}^* | | \bar{f}_0 | &\leq c (sLb)^2 \frac{1}{n} \log \frac{2}{\delta} \\
\bar{f}^{*2} &\leq c (sLb)^2 \frac{1}{n} \log \frac{2}{\delta}
\end{align*}

Therefore, with probability at least $1 - 2\delta$,
\[
\|f_0 - f^*\|_n^2 - c (sLb)^2 \frac{1}{n} \log \frac{2}{\delta} \leq
    \| f_0 - f^* + \bar{f}^* \|_n^2 \leq 
\|f_0 - f^*\|_n^2 + c (sLb)^2 \frac{1}{n} \log \frac{2}{\delta}
\]

### 2014-05-05 tex/scam/paper.tex
paper update
paper modifications

@@

@@

\begin{abstract}
  We consider the problem of estimating a sparse convex function of
  many variables.  In constrast to classical nonparametric
  regression with smoothness constraints, we show that convexity is
  additively faithful---it suffices to estimate a convex additive
  model for variable selection.  We develop algorithms for estimating
  sparse convex additive models, including an approach using iterative
  quadratic programming.  Supporting experiments and statistical
  theory are presented, showing variable selection consistency in
  dimensions that can scale exponentially in the sample size.  An
  attractive feature of this framework is the lack of tuning parameters
  for smoothness.
\end{abstract}
\vskip10pt

@@

\input{introduction}
\input{related_work}
\input{summary}
\input{additive_faithful}
\input{optimization}
\input{sparsistency}
\input{experiments}
\input{discussion}

>>>>

\usepackage{yhmath}

@@

% min's macros
\mathchardef\mh="2D

@@

\begin{abstract}
We consider the problem of estimating a convex function of several variables from noisy values of the function at a finite sample of input points. 
\end{abstract}
\vskip10pt

@@

\input{introduction}
\input{related_work}
\input{summary}
\input{additive_faithful}
\input{estimation}
\input{optimization}
\input{sparsistency}
\input{experiments}
\input{discussion}

### 2014-05-05 tex/scam/sparsistency.tex
paper modifications

We divide our analysis into two parts. We first establish a sufficient deterministic condition for sparsistency.  We then consider the
stochastic setting and argue that the deterministic conditions hold with high probability.

@@

\begin{definition}
\label{def:restricted_regression}
In \emph{restricted regression}, we restrict the indices $k$ in
optimization (\ref{opt:alternate_opt}) to lie in the set $S$ instead of ranging from $1,...,p$. 
\end{definition}

Our analysis then differs from the now-standard ``primal-dual witness
technique''~\cite{Wain:09a}. Primal-dual witness explicitly solves all the dual variables, but because our optimization program is more complex, we do not solve the dual variables on $S$; we instead write the dual variables on $S^c$ as a function of the restricted regression \emph{residual}, which is implicitly a function of the dual variables on $S$.

\begin{theorem} (Deterministic setting)
\label{thm:deterministic}
Let $\{\hat{d}_k \}_{k \in S}$ be a minimizer of the restricted regression, that is, the solution to optimization (\ref{opt:alternate_opt}) where we restrict $k \in S$. 
Let $\hat{r} \coloneqq Y - \sum_{k \in S} \bar{\Delta}_k \hat{d}_k$ be the restricted regression residual. \\

@@

Theorem~\ref{thm:deterministic} allows us to analyze false negative
rates and false positive rates separately. To control false positives,
we analyze when the condition on $\lambda_n$ is fulfilled for all $j$ and all $k \in S^c$. To control false negatives, we analyze the restricted regression.

@@

Suppose $\lambda \leq \mathbf{c} sLb  \sqrt{\frac{1}{n} \log^2 np}$ and suppose $n$ is large enough such that $(Lb)^3 \sigma \sqrt{\frac{s^5}{n^{4/5}} \log^2 np} \leq 1$.\\

Suppose 
$\frac{\alpha_f}{\sigma} \geq \mathbf{c} (Lb)^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$ and $\frac{\alpha_g^2}{\sigma} \geq \mathbf{c} (Lb)^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 2np}$.\\

@@

Suppose 
$\frac{\alpha_f}{\sigma} \geq \mathbf{c} (Lb)^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$ and $\frac{\alpha_g^2}{\sigma} \geq \mathbf{c} (Lb)^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 2np}$.\\

>>>>

We divide our analysis into two parts. We first establish a sufficient deterministic condition for sparsistency.  We then consider the
stochastic setting and argue that the deterministic conditions hold with high probability. In all of our results and analysis, we let $c, C$ represent absolute constants; the actual values of $c,C$ could change from line to line.

@@

\begin{definition}
\label{def:restricted_regression}
We define as \emph{restricted regression} where we restrict the indices $k$ in
optimization (\ref{opt:alternate_opt}) to lie in the set $S$ instead of ranging from $1,...,p$:
\[
\min_{d_k} \frac{1}{n} \Big\| Y - \sum_{k \in S} \bar{\Delta}_k d_k \Big\|_2^2 + 
   \lambda_n \sum_{k \in S} \| \bar{\Delta}_k d_k \|_\infty \quad \trm{such that} \, d_{k,1}, ..., d_{k,n-1} \geq 0
\]
\end{definition}

\begin{theorem} (Deterministic setting)
\label{thm:deterministic}
Let $\{\hat{d}_k \}_{k \in S}$ be a minimizer of the restricted regression as defined above.
Let $\hat{r} \coloneqq Y - \sum_{k \in S} \bar{\Delta}_k \hat{d}_k$ be the restricted regression residual. \\

@@

Theorem~\ref{thm:deterministic} allows us to analyze false negative
rates and false positive rates separately. To control false positives,
we analyze when the condition on $\lambda_n$ is fulfilled for all $j$ and all $k \in S^c$. To control false negatives, we analyze the restricted regression. \\

The proof of theorem~\ref{thm:deterministic} looks at KKT conditions of optimization~\ref{opt:alternate_opt}, similar to the now standard \emph{primal-dual witness} technique~\cite{wainwright2009sharp}. We cannot derive analogous \emph{mutual incoherence} conditions because the estimation is nonparametric -- even the low dimensional restricted regression has $s(n-1)$ variables. The details of the proof are in section~\ref{sec:deterministic_proof} of the Appendix.

@@

Suppose $\lambda \leq c sLb  \sqrt{\frac{1}{n} \log^2 np}$ and suppose $n$ is large enough such that $(Lb)^3 \sigma \sqrt{\frac{s^5}{n^{4/5}} \log^2 np} \leq 1$.\\

Suppose 
$\frac{\alpha_f}{\sigma} \geq c (Lb)^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$ and $\frac{\alpha_g^2}{\sigma} \geq c (Lb)^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 2np}$.\\

@@

Suppose 
$\frac{\alpha_f}{\sigma} \geq c (Lb)^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 np}$ and $\frac{\alpha_g^2}{\sigma} \geq c (Lb)^3 \sqrt{\frac{s^5}{n^{4/5}} \log^2 2np}$.\\
